Propositions as Sessions, Mechanically

### 2015-04-23 paper/presentation.tex
Progress being made on presentation structure.

\begin{frame}
another frame for cp this time its well typing time
\end{frame}

\begin{comment}
lets take a look at cp's typing rules. here we used a well typed relation on
the process terms of cp. we require additional assumptions for environment
ordering and
\end{comment}

\begin{frame}
an example of GV
\end{frame}

@@

@@

@@

>>>>

\subsection{CP}

\begin{frame}[fragile]
\oldframetitle{CP Rules: Formal vs. Informal Comparison}
\begin{tabular}{lc}
\begin{coqp}
Inductive cp_rule : proc -> penv -> Prop :=
  | $\cdots$
  | cp_cut :
      forall (L:atoms) P Q A $\Gamma$ $\Delta$P $\Delta$Q
             (PER: Permutation $\Gamma$ ($\Delta$P ++ $\Delta$Q))
             (CPP: forall (x:atom) (NL: x $\notin$ L),
                     (open_proc P x) $\tpcp$ (x $\sim$ A) ++ $\Delta$P)
             (CPQ: forall (x:atom) (NL: x $\notin$ L),
                (open_proc Q x) $\tpcp$ (x $\sim$ $\dualbt{A}$) ++ $\Delta$Q),
        $\nu$ A.(P $\mid$ Q) $\tpcp$ $\Gamma$
  | $\cdots$
\end{coqp} &
\begin{math}
\colored
\inference{
  \tm{P} \tpvdash \tp{\Gamma \comma \tmof{x}A}
  &
  \tm{Q} \tpvdash \tp{\Delta \comma \tmof{x}\dualbt{A}}
}{}{
  \tm{\nu x \of{A}.(P \mid Q)} \tpvdash \tp{\Gamma \comma \Delta}
}
\end{math}
\end{tabular}

%% \begin{coqp}
%% Inductive cp_rule : proc -> penv -> Prop :=
%%   | $\cdots$
%%   | cp_cut :
%%       forall (L:atoms) P Q A $\Gamma$ $\Delta$P $\Delta$Q
%%              (PER: Permutation $\Gamma$ ($\Delta$P ++ $\Delta$Q))
%%              (CPP: forall (x:atom) (NL: x $\notin$ L),
%%                      (open_proc P x) $\tpcp$ (x $\sim$ A) ++ $\Delta$P)
%%              (CPQ: forall (x:atom) (NL: x $\notin$ L),
%%                 (open_proc Q x) $\tpcp$ (x $\sim$ $\dualbt{A}$) ++ $\Delta$Q),
%%         $\nu$ A.(P $\mid$ Q) $\tpcp$ $\Gamma$
%%   | $\cdots$
%% \end{coqp}
\end{frame}

\begin{comment}
lets take a look at cp's typing rules. here we used a well typed relation on
the process terms of cp. we require additional assumptions for environment
ordering and more attention is paid to the opening of subprocesses. this
presents the informal and formal definitions of cut. There is no overhead when
introducing binders to the subprocesses or for environment ordering, but apart
from these representation issues the rules look similar which could assist the
uptake of such formal tools by programming language researchers.
\end{comment}

\defverbatim[colored]\subred{
\begin{coq}
Theorem proc_sub_red:
  forall $\Gamma$ P Q
         (WT: P $\tpvdash_{cp}$ $\Gamma$)
         (RED: P $\becomes$ Q),
    Q $\tpvdash_{cp}$ $\Gamma$.
\end{coq}
}

\begin{frame}
\oldframetitle{Subject Reduction in CP}
\subred
\begin{itemize}
\item {\fontsize{6}{7.2}\selectfont blah one}
\item blah two
\item blah three
\item blah four
\item blah five
\item blah six
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Subject Reduction in CP}
\[\colored
\begin{array}{c}
\mbox{Subject reduction} = \left\{ \begin{array}{ll}
                                   \mbox{Principal cut reductions}~(\beta)\\
                                   \mbox{Commuting Conversions}~(\kappa)
                                   \end{array} \right.
\\~\\
(\kappa_{\otimes1}) \quad
\tm{\nu z\Of{C}.(x[y].(P \mid Q) \mid R)}
\quad \becomes \hfill
\hfill \tm{x[y].(\nu z\Of{C}.(P \mid R) \mid Q)}
\end{array}
\]
\end{frame}

\begin{comment}
Subject reduction in CP proceeds by cut reductions of the logical operators
against their duals and \textit{commuting conversions} as well as some other
rules. Commuting conversions push a cut inside a logical operator and the
intuition is that they permit further communication to occur which was guarded
by a cut.
\end{comment}

\subsection{GV}

\begin{frame}
GV
\end{frame}

@@

\subsection{Translation}

@@

\subsection{Issues}

@@

\section{Future Work}
